Characterisation of transient resonances in extreme-mass-ratio-inspirals

### 2014-08-06 asymptotic.tex
Small tweaks

The following derivation is reproduced from Berry~\cite{BerryThesis2013} and is based upon the analysis of Kevorkian~\cite{Kevorkian1987}.\footnote{The same two time-scale theory underpins the analysis of Hinderer and Flanagan~\cite{Hinderer2008}, but this explicitly ignores resonances.} Small adjustments have been made to adapt to the specific problem of GW inspiral, but the general argument is unchanged. A similar derivation can be found by van de Meent~\cite{VanDeMeent2014}.

@@

As a final step in understanding our result, we switch from Mino time to coordinate time. An appropriate redefinition of the forcing functions can be done by scaling by $\Gamma$, we define
\begin{equation}
F_a^{(1)} = \dfrac{G_a^{(1)}}{\Gamma},
\end{equation}
such that the equation of motion becomes
\begin{equation}
\left\langle \diff{\mathcal{I}_a}{t}\right\rangle_{q'} =  \eta\sum_s F_{a,\,s}^{(1)}(\boldsymbol{\mathcal{I}})\exp(is q) + \order{\eta^2}.
\end{equation}
Here we have made the averaging over $q'$ explicit to show that the equation is only defined as an orbital average: not only does our asymptotic expansion average out oscillations over an orbit in $q'$, but in converting from $\lambda$ to $t$ we have used $\Gamma$ which is an orbital average.
From \eqnref{omega-series}, we recognise that
\begin{equation}
\varpi_1 = \partialdiff{\omega}{\widetilde{\lambda}} = \dfrac{\Gamma^2}{\eta}\left\langle\dot{\Omega}\right\rangle_{q'}.
\end{equation}
We have used the averaged form of $\dot{\Omega}(t)$ as this is appropriate. Using these to adapt equations (\ref{eq:J-1/2}) and (\ref{eq:jumps}), we obtain
\begin{align}
\Delta \mathcal{I}_a = {} & \eta\sum_{s\,\neq\,0}F_{a,\,s}^{(1)}(\boldsymbol{\mathcal{I}}_\star)\sqrt{\dfrac{2\pi}{\left|s \langle\dot{\Omega}\rangle_{q'}\right|}} \nonumber \\*
 {} & \times \left.\exp\left[i\left(s \widehat{\kappa}_0 + \dfrac{\pi}{4}\sgn s\dot{\Omega}\right)\right]\right. \\
 = {} & \eta\sum_{s\,\neq\,0}F_{a,\,s}^{(1)}(\boldsymbol{\mathcal{I}}_\star)\tau_{\mathrm{res},\,s}\exp\left[i\left(s \widehat{\kappa}_0 + \dfrac{\pi}{4} \sgn s\dot{\Omega} \right)\right],
\end{align}
using \eqnref{T-res-s} and representing the values on resonance of $E$, $L_z$ and $Q$ with $\boldsymbol{\mathcal{I}}_\star$.

>>>>

The following derivation is reproduced from Berry~\cite{BerryThesis2013}. It is is based upon the analysis of Kevorkian~\cite{Kevorkian1987}; small adjustments have been made to adapt to the specific problem of GW inspiral, but the general argument is unchanged.\footnote{The same two time-scale theory underpins the analysis of Hinderer and Flanagan~\cite{Hinderer2008}, but this explicitly ignores resonances.} A similar derivation can be found by van de Meent~\cite{VanDeMeent2014}.

@@

As a final step in understanding our result, we switch from Mino time to coordinate time. An appropriate redefinition of the forcing functions can be done by scaling by $\Gamma$, we define
\begin{equation}
F_a^{(1)} = \dfrac{G_a^{(1)}}{\Gamma},
\end{equation}
such that the equation of motion becomes
\begin{equation}
\left\langle \diff{\mathcal{I}_a}{t}\right\rangle_{q'} =  \eta\sum_s F_{a,\,s}^{(1)}(\boldsymbol{\mathcal{I}})\exp(is q) + \order{\eta^2}.
\end{equation}
Here we have made the averaging over $q'$ explicit to show that the equation is only defined as an orbital average: not only does our asymptotic expansion average out oscillations over an orbit in $q'$, but in converting from $\lambda$ to $t$ we have used $\Gamma$ which is an orbital average.
From \eqnref{omega-series}, we recognise that
\begin{equation}
\varpi_1 = \partialdiff{\omega}{\widetilde{\lambda}} = \dfrac{\Gamma^2}{\eta}\left\langle\dot{\Omega}\right\rangle_{q'}.
\end{equation}
We have used the averaged form of $\dot{\Omega}(t)$ as this is appropriate. Using these to adapt equations (\ref{eq:J-1/2}) and (\ref{eq:jumps}), we obtain
\begin{align}
\Delta \mathcal{I}_a = {} & \eta\sum_{s\,\neq\,0}F_{a,\,s}^{(1)}(\boldsymbol{\mathcal{I}}_\star)\left[\dfrac{2\pi}{\left|s \left\langle\dot{\Omega}\right\rangle_{q'}\right|}\right]^{1/2} \nonumber \\*
 {} & \times \left.\exp\left[i\left(s \widehat{\kappa}_0 + \dfrac{\pi}{4}\sgn s\dot{\Omega}\right)\right]\right. \\
 = {} & \eta\sum_{s\,\neq\,0}F_{a,\,s}^{(1)}(\boldsymbol{\mathcal{I}}_\star)\tau_{\mathrm{res},\,s}\exp\left[i\left(s \widehat{\kappa}_0 + \dfrac{\pi}{4} \sgn s\dot{\Omega} \right)\right],
\end{align}
using \eqnref{T-res-s} and representing the values on resonance of $E$, $L_z$ and $Q$ with $\boldsymbol{\mathcal{I}}_\star$.
